plyr: Split-Apply-Combine for Mortals

### 2013-10-20 _knitr-posts/2013-10-20-plyr.Rmd
Left-align table headers and re-knit

object type| data frame | list    | array
-----------|------------|---------|--------
data frame | `ddply`    | `ldply` | `adply`
list       | `dlply`    | `llply` | `alply`
array      | `daply`    | `laply` | `aaply`

>>>>

object type |data frame  |list     |array
------------|------------|---------|--------
data frame  | `ddply`    | `ldply` | `adply`
list        | `dlply`    | `llply` | `alply`
array       | `daply`    | `laply` | `aaply`
